\documentclass[11pt,letter,twoside]{mc2011}
\usepackage{amsmath}
\usepackage{array}
%\usepackage{color}
%\usepackage{graphicx}
\usepackage{float} %utiliser H pour forcer à mettre l'image où on veut
\usepackage{lscape} %utilisation du mode paysage
\usepackage{mathbbol} % permet d'avoir le vrai symbol pour les reels grace a mathbb
\usepackage{enumerate}
\usepackage{marvosym}	
\usepackage{moreverb} % permet d'utiliser verbatimtab : conservation la tabulation 


\setlength {\textwidth}{16cm}
\setlength {\textheight}{21cm} 
\setlength {\oddsidemargin}{0cm}
\setlength{\headsep}{5pt} 

\newcommand\bn{\boldsymbol{\nabla}}
\newcommand\bo{\boldsymbol{\Omega}}
\newcommand\br{\mathbf{r}}
\newcommand\la{\left\langle}
\newcommand\ra{\right\rangle}
\newcommand\bs{\boldsymbol}
\newcommand\red{\textcolor{red}}

\renewcommand{\(}{\left(}
\renewcommand{\)}{\right)}
\renewcommand{\[}{\left[}
\renewcommand{\]}{\right]}

\newtheorem{theorem}{Theorem}[section]

\usepackage[numbers,sort&compress]{natbib}

\usepackage{fancyhdr,lastpage}

\usepackage[dvips]{graphicx,color}

\pagestyle{fancy}

\globalmc2011

\begin{document}
\title{Restricted Galerkin quadrature for coupled photon-electron transport.}
\author{
    \textbf{Bruno Turcksin, Jean Ragusa, Jim Morel and Damien
    Lebrun-Grandie}\\
    Texas A\&M University, Department of Nuclear Engineering\\
    College Sation, Texas 77843-3133\\
    turcksin@neo.tamu.edu; ragusa@ne.tamu.edu; morel@ne.tamu.edu;
    lebrungd@neo.tamu.edu
}
\date{}
\maketitle

\thispagestyle{empty}

\begin{abstract}
Use 8.5 x 11 paper size, with 1" margins on all sides. A required 200-250 word abstract starts on this line.  
Leave two blank lines before ABSTRACT and one after.  Use 10 point Times New Roman here and single 
(10 point) spacing.  The abstract is a very brief summary highlighting main accomplishments, what is new, 
and how it relates to the state-of-the-art.

\keywords{Galerkin quadrature, electron, radiotherapy}

\end{abstract}

\newcommand\authorname{Bruno Turcksin et al.}
\newcommand\shorttitlename{Restricted Galerkin quadrature for coupled
photon-electron transport.}

\fancymc2011

% Introduction
\input{introduction}

% Equations
\input{equations}

% Memory
\input{memory}

% Results
\input{results}

\bibliographystyle{unsrt}
\bibliography{biblio}

\end{document}
